Price of Anarchy for Mean Field Games

### 2018-08-03 PoA.tex
modified Prop 2 and Corollary 1

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation*}
\begin{split}
    \left[s\bar{q}(s-1)+\bar{b}_1\bar{\eta}_t^{MKV}\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    (b^{MFG}-b^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
\end{split}
\end{equation*}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $c^{MFG}-c^{MKV}=b^{MFG}-b^{MKV}$, the result is clear.
\end{proof}

\begin{corollary}
Assuming (\ref{eq:assumptions}), if furthermore, $s\bar{q}(s-1)=0$, $\bar{b}_1=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
then $PoA=1$.
\label{corollary_1}
\end{corollary}

>>>>

\begin{proposition}
Assuming (\ref{eq:assumptions}), if furthermore,
\begin{equation*}
\begin{split}
    \left[\bar{b}_1\bar{\eta}_t^{MKV}+s\bar{q}(s-1)\right]\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    (c^{MFG}-c^{MKV})(b_2+\bar{b}_2)\bar{\eta}_t^{MKV}\bar{x}_t^{MKV}&=0,\ \forall t \in [0,T] \\
    s_T\bar{q}_T(s_T-1)\bar{x}_T^{MKV}&=0,
\end{split}
\end{equation*}
then $PoA=1$.
\label{eq:lq_prop}
\end{proposition}

\begin{proof}
    Comparing the FBSDE systems (\ref{eq:FBSDE_EMFG}) and (\ref{eq:FBSDE_EMKV}), and using the fact that $b^{MFG}-b^{MKV}=c^{MFG}-c^{MKV}$, the result is clear.
\end{proof}

\begin{corollary}
	Assuming (\ref{eq:assumptions}), if furthermore, $\bar{b}_1=0$, $s\bar{q}(s-1)=0$, $\frac{b_2(r+\bar{r}(1-\bar{s})^2)}{(b_2+\bar{b}_2)(r+\bar{r}(1-\bar{s}))}=1$, and $s_T\bar{q}_T(s_T-1)=0$,
	then $PoA=1$.
	\label{corollary_1}
\end{corollary}
